\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors

### 2022-06-16 Manuscript/Lanuza_et_al_2021.Rmd
edits

Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context. Although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach. We found support to this trait association and show that other reproductive traits and plant form and size related traits also covariate along this axis. For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number. Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors. Therefore, our results highlight the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.

>>>>

Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context. Although the negative correlation between flower number and flower size has received substantial attention [@worley2000; @sargent2007; @kettle2011], it has only been investigated across a few hundred of Angiosperm species with a two-trait approach. We found support to this trait association and show that other life history traits also covariate along this axis. For example, our study complements previous evidence that links breeding systems and life forms [@petit2006; @friedman2020] by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number. Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display [@goodwillie2010] where species with high pollinator dependence have greater allocation of resources to attract floral visitors. Thus, our results highlight the presence of global reproductive trait covariation patterns across flowering plants that are shaped by floral visitors and are likely to impose constraints to the whole spectrum of trait variation.

### 2022-06-16 Manuscript/Lanuza_et_al_2021.tex
edits

Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context. Although the negative correlation between flower number and flower size has received substantial attention (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}; \protect\hyperlink{ref-worley2000}{Worley et al., 2000}), it has only been investigated across a few hundred of Angiosperm species with a two-trait approach. We found support to this trait association and show that other reproductive traits and plant form and size related traits also covariate along this axis. For example, our study complements previous evidence that links breeding systems and life forms (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}) by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number. Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) where species with high pollinator dependence have greater allocation of resources to attract floral visitors. Therefore, our results highlight the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.

>>>>

Our study provides solid evidence for several widely discussed trait associations with the help of a great diversity of phylogenetic lineages (170 families and over 1000 species) within a multitrait context. Although the negative correlation between flower number and flower size has received substantial attention (\protect\hyperlink{ref-kettle2011}{Kettle et al., 2011}; \protect\hyperlink{ref-sargent2007}{Sargent et al., 2007}; \protect\hyperlink{ref-worley2000}{Worley et al., 2000}), it has only been investigated across a few hundred of Angiosperm species with a two-trait approach. We found support to this trait association and show that other life history traits also covariate along this axis. For example, our study complements previous evidence that links breeding systems and life forms (\protect\hyperlink{ref-friedman2020}{Friedman, 2020}; \protect\hyperlink{ref-petit2006}{Petit \& Hampe, 2006}) by showing that most species with unisexual flowers are concentrated in the trait space and are associated with woody life forms with high flower number. Moreover, we also provide broad support for the previously documented positive association between outcrossing rate and floral display (\protect\hyperlink{ref-goodwillie2010}{Goodwillie et al., 2010}) where species with high pollinator dependence have greater allocation of resources to attract floral visitors. Thus, our results highlight the presence of global reproductive trait covariation patterns across flowering plants that are shaped by floral visitors and are likely to impose constraints to the whole spectrum of trait variation.

that are shaped by the interaction between plants and floral visitors.

that is mediated by the interaction with floral visitors wich ultimately

need to be included when exploring the global spectrum of trait variation of flowering plants.

are mediated by floral visitors.

Quizas frase para conclusion:

Therefore, our results highlight the need to account in the global spectrum of plant trait variation the overlook reproductive trait covariation patterns that are ultimately impacted by their interaction with floral visitors.

that life history strategies in flowering plants are constraint by reproductive trait covariation patterns that are mediated by floral visitors.

the presence of worldwide reproductive trait covariation patterns that are mediated by floral visitors.
